---
title: "DATA607-LAB9"
author: "Biyag Dukuray"
output: html_document
date: "2024-03-20"
---

## Assignment – Web APIs

**The New York Times web site provides a rich set of APIs, as described here:** https://developer.nytimes.com/apis
**You’ll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.**

```{r}
library(jsonlite)
library(httr)
library(purrr)

url <- "https://api.nytimes.com/svc/books/v3/lists/names.json?api-key=POly7DhxmA60a8GvBxlAvolA9ZLaQvkA"
json_data <- fromJSON(url)
raw_data <- json_data$results
colnames(raw_data)
```

**I entered the raw JSON data from the API into a dataframe that I named raw_data. Upon doing this, I extracted the column names to see how this dataframe should be structured. I then extracted the specific columns and entered this data into a dataframe to this display my API data.**

```{r}

list_name <- raw_data$list_name
display_name <- raw_data$display_name
list_name_encoded <- raw_data$list_name_encoded
oldest_published_date <- raw_data$oldest_published_date
newest_published_date <- raw_data$newest_published_date
updated <- raw_data$updated


APIdf <- data.frame(
  list_name = list_name,
  display_name = display_name,
  list_name_encoded = list_name_encoded,
  oldest_published_date = oldest_published_date,
  newest_published_date = newest_published_date,
  updated = updated)
```

**Upon completing this data tidying and transformation, my data was entered into a dataframe that I named 'APIdf' This displays the data that the API has provided to me**

```{r}
# Displaying the dataframe
print(APIdf)
```

